Comparison to Christensen et al. 2018

### 2019-02-05 doc/paper-comparison.Rmd
build vignettes and push doc

---
title: "Paper comparison (cleaned up)"
author: "Renata Diaz"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{paper-comparison}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("weecology/LDATS")
install.packages('here')
```

@@

paper_filepath <- here::here('vignette', 'christensenetal-comparison-files', 'christensenetal-2018-files')
test_filepath <- here::here('vignette', 'christensenetal-ristensenetal-comparison-files', 'christensenetal-2018-files', 'rodent_LDA_analysis.r')

@@

```{r Paper data}
source(here::here('vignette', 'christensenetal-comparison-files', 'christensenetal-2018-files', 'rodent_data_for_LDA.r'))

@@

While LDATS can run start-to-finish with `LDATS::LDA_TS`, here we will work through the process function-by-function to isolate differences with the paper. For an illustration of `LDA_TS`, see the `codebase` vignette.

@@

save(ldats_ldas, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_ldas.Rds'))
save(ldats_lda_selected, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_lda_selected.Rds'))

@@

```{r paper LDAs, eval = F}
source(here::here('vignette', 'christensenetal-comparison-files', 'christensenetal-2018-files', 'AIC_model_selection.R'))
source(here::here('vignette', 'christensenetal-comparison-files', 'christensenetal-2018-files', 'LDA-distance.R'))

@@

save(ldamodel,file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_ldamodel.Rds'))
```

@@

load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_lda_selected.Rds'))
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_ldamodel.Rds'))

@@

```{r plot LDAs}
# Paper
plot(ldamodel, cols = NULL, option = "D")

# LDATS
plot(ldats_lda_selected[[1]], cols = NULL, option = "D")
```

@@

The paper method finds 4 topics and LDATS finds 6. This is because of an update to the model selection procedure. The paper conservatively overestimates the number of parameters and therefore overpenalizes AIC for models with more topics. For this vignette, we will compare the results from using both LDA models.

@@

The paper changepoint model weighted all sample periods equally, wheras LDATS can weight sample periods according to how many individuals were captured (controlled by the `document_term_weights`). We now believe it is more appropriate to weight periods proportional to captures, and this is what we recommend for LDATS users. For the purposes of comparison, we will continue set all weights = 1 for both changepoint models. For an example of LDATS run with proportional weights, see the rodents vignette. [?]

@@

#### Load LDA ####
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_lda_selected.Rds'))

@@

```{r run LDATS LDA and paper cpt, eval = F}
#### Run changepoint ####
source(here::here('vignette', 'christensenetal-comparison-files', 'christensenetal-2018-files', 'changepointmodel.r'))

@@

# run models with 1, 2, 3, 4, 5, 6 changepoints
cp_results_rodent = changepoint_model(ldats_lda_selected[[1]], x, 1, weights = rep(1,length(year_continuous)))
save(cp_results_rodent, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_1.Rds'))
rm(cp_results_rodent)

cp_results_rodent2 = changepoint_model(ldats_lda_selected[[1]], x, 2, weights = rep(1,length(year_continuous)))
save(cp_results_rodent2, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_2.Rds'))
rm(cp_results_rodent2)

cp_results_rodent3 = changepoint_model(ldats_lda_selected[[1]], x, 3, weights = rep(1,length(year_continuous)))
save(cp_results_rodent3, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_3.Rds'))
rm(cp_results_rodent3)

cp_results_rodent4 = changepoint_model(ldats_lda_selected[[1]], x, 4, weights = rep(1,length(year_continuous)))
save(cp_results_rodent4, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_4.Rds'))
rm(cp_results_rodent4)

cp_results_rodent5 = changepoint_model(ldats_lda_selected[[1]], x, 5, weights = rep(1,length(year_continuous)))
save(cp_results_rodent5, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_5.Rds'))
rm(cp_results_rodent5)

cp_results_rodent6 = changepoint_model(ldats_lda_selected[[1]], x, 6, weights = rep(1,length(year_continuous)))
save(cp_results_rodent6, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_6.Rds'))
rm(cp_results_rodent6)
```

```{r select LDATS LDA and paper cpt}
#### Changepoint model selection ####
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_1.Rds'))
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_2.Rds'))
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_3.Rds'))
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_4.Rds'))
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_5.Rds'))
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_6.Rds'))

@@

#### Load LDA ####
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_ldamodel.Rds'))

@@

```{r run paper LDA and paper cpt, eval = F}
#### Run changepoint ####
source(here::here('vignette', 'christensenetal-comparison-files', 'christensenetal-2018-files', 'changepointmodel.r'))

@@

# run models with 1, 2, 3, 4, 5, 6 changepoints
cp_results_rodent = changepoint_model(ldamodel, x, 1, weights = rep(1,length(year_continuous)))
save(cp_results_rodent, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_paper1.Rds'))
rm(cp_results_rodent)

cp_results_rodent2 = changepoint_model(ldamodel, x, 2, weights = rep(1,length(year_continuous)))
save(cp_results_rodent2, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_paper2.Rds'))
rm(cp_results_rodent2)

cp_results_rodent3 = changepoint_model(ldamodel, x, 3, weights = rep(1,length(year_continuous)))
save(cp_results_rodent3, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_paper3.Rds'))
rm(cp_results_rodent3)

cp_results_rodent4 = changepoint_model(ldamodel, x, 4, weights = rep(1,length(year_continuous)))
save(cp_results_rodent4, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_paper4.Rds'))
rm(cp_results_rodent4)

cp_results_rodent5 = changepoint_model(ldamodel, x, 5, weights = rep(1,length(year_continuous)))
save(cp_results_rodent5, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_paper5.Rds'))
rm(cp_results_rodent5)

cp_results_rodent6 = changepoint_model(ldamodel, x, 6, weights = rep(1,length(year_continuous)))
save(cp_results_rodent6, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_paper6.Rds'))
rm(cp_results_rodent6)
```

```{r select paper LDA and paper cpt}
#### Changepoint model selection ####
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_1.Rds'))
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_2.Rds'))
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_3.Rds'))
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_4.Rds'))
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_5.Rds'))
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_6.Rds'))

@@

save(ldats_ldats_cpt, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_ldats.Rds'))
rm(ldats_ldats_cpt)
rm(ldats_lda_selected)
```

```{r load LDATS LDA and LDATS changepoint, include = F}
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_ldats.Rds'))
```

@@

save(ldats_ldats_cpt_selected, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_ldats_selected.Rds'))

@@

save(paper_ldats_cpt, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_ldats.Rds'))
rm(paper_ldats_cpt)
rm(ldamodel)
```

```{r load paper LDA and LDATS changepoint, include = F}
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_ldats.Rds'))
```

@@

Unlike the paper changepoint model, LDATS can recognize that sampling periods may not be equidistant, and can place changepoint estimates at new moons if they fall between nonconsecutive sampling periods. We can estimate the dates corresponding to those new moons.

@@

save(paper_ldats_cpt_selected, file = here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_ldats_selected.Rds'))

@@

```{r report cpt dates, include = F}

@@

The choice of LDA has more influence on the changepoint locations than the choice of changepoint model - probably because the LDATS LDA has 6 topics, and the paper LDA has 4.

@@

```{r load cpts to plot, include = F}
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_ldats_selected.Rds'))
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_ldats_selected.Rds'))
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_4.Rds'))
paper_paper_cpt_selected <- cp_results_rodent4
load(here::here('vignette', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_4.Rds'))
ldats_paper_cpt_selected <- cp_results_rodent4

```{r plot cpts}

plot(ldats_ldats_cpt_selected)

source(here::here('vignette', 'christensenetal-comparison-files', 'christensenetal-2018-files', 'LDA_figure_scripts.R'))
source(here::here('vignette', 'christensenetal-comparison-files', 'christensenetal-2018-files', 'changepointmodel.r'))
paper_cpts = find_changepoint_location(paper_paper_cpt_selected)
paper_cpt_plot = get_ll_non_memoized_plot(ldamodel,x,paper_cpts,make_plot=T,weights=rep(1,length(year_continuous)))
annual_hist(paper_paper_cpt_selected, year_continuous)
paper_cpt_plot

ntopics = 6
ldats_cpts = find_changepoint_location(ldats_paper_cpt_selected)
ldats_cpt_plot = get_ll_non_memoized_plot(ldats_lda_selected[[1]],x,ldats_cpts,make_plot=T,weights=rep(1,length(year_continuous)))
annual_hist(ldats_paper_cpt_selected, year_continuous)
ldats_cpt_plot
```

>>>>

---
title: "Comparison to Christensen et al. 2018"
author: "Renata Diaz"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{paper-comparison}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("weecology/LDATS")
```

@@

paper_filepath <- here::here('vignettes', 'christensenetal-comparison-files', 'christensenetal-2018-files')
test_filepath <- here::here('vignettes', 'christensenetal-ristensenetal-comparison-files', 'christensenetal-2018-files', 'rodent_LDA_analysis.r')

@@

```{r Paper data}
source(here::here('vignettes', 'christensenetal-comparison-files', 'christensenetal-2018-files', 'rodent_data_for_LDA.r'))

@@

While LDATS can run start-to-finish with `LDATS::LDA_TS`, here we will work through the process function-by-function to isolate differences with the paper. For a breakdown of the `LDA_TS` pipeline, see the [`codebase` vignette](https://weecology.github.io/LDATS/articles/LDATS_codebase.html).

@@

save(ldats_ldas, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_ldas.Rds'))
save(ldats_lda_selected, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_lda_selected.Rds'))

@@

```{r paper LDAs, eval = F}
source(here::here('vignettes', 'christensenetal-comparison-files', 'christensenetal-2018-files', 'AIC_model_selection.R'))
source(here::here('vignettes', 'christensenetal-comparison-files', 'christensenetal-2018-files', 'LDA-distance.R'))

@@

save(ldamodel,file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_ldamodel.Rds'))
```

@@

load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_lda_selected.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_ldamodel.Rds'))

@@

#### Paper LDA
```{r plot paper LDA, fig.width=6, fig.height=6}
# Paper
plot(ldamodel, cols = NULL, option = "D")

#### LDATS LDA
```{r plot LDATS LDA, fig.width=6, fig.height=6}
# LDATS
plot(ldats_lda_selected[[1]], cols = NULL, option = "D")
```

@@

The paper method finds 4 topics and LDATS finds 6. This is because of an update to the model selection procedure. The paper conservatively overestimates the number of parameters (by counting all of the variational parameteres) and therefore overpenalizes the AIC for models with more topics. Comparatively, the LDATS method now uses the number of parameters remaining after the variational approximation, as returned by the LDA object. For this vignette, we will compare the results from using both LDA models.

@@

Having divided the data to generate catch-per-effort, the paper changepoint model weighted all sample periods equally. In comparison, LDATS does not force an equal weighting, but assumes that as default, and can weight sample periods according to how many individuals were captured (controlled by the `weights` argument to `LDA_TS`, and easily calculated for a document-term matrix using `document_term_weights`. We now believe it is more appropriate to weight periods proportional to captures in the time series (despite the LDA function returning only proportions of each topic), and this is what we recommend for LDATS users. For the purposes of comparison, however, we will continue set all weights = 1 for both changepoint models. For an example of LDATS run with proportional weights, see the [rodents vignette](https://weecology.github.io/LDATS/articles/rodents-example.html).

@@

#### Load LDA ####
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_lda_selected.Rds'))

@@

```{r run LDATS LDA and paper cpt, eval = F}
#### Run changepoint ####
source(here::here('vignettes', 'christensenetal-comparison-files', 'christensenetal-2018-files', 'changepointmodel.r'))

@@

# run models with 1, 2, 3, 4, 5, 6 changepoints
cp_results_rodent = changepoint_model(ldats_lda_selected[[1]], x, 1, weights = rep(1,length(year_continuous)))
save(cp_results_rodent, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_1.Rds'))
rm(cp_results_rodent)

cp_results_rodent2 = changepoint_model(ldats_lda_selected[[1]], x, 2, weights = rep(1,length(year_continuous)))
save(cp_results_rodent2, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_2.Rds'))
rm(cp_results_rodent2)

cp_results_rodent3 = changepoint_model(ldats_lda_selected[[1]], x, 3, weights = rep(1,length(year_continuous)))
save(cp_results_rodent3, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_3.Rds'))
rm(cp_results_rodent3)

cp_results_rodent4 = changepoint_model(ldats_lda_selected[[1]], x, 4, weights = rep(1,length(year_continuous)))
save(cp_results_rodent4, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_4.Rds'))
rm(cp_results_rodent4)

cp_results_rodent5 = changepoint_model(ldats_lda_selected[[1]], x, 5, weights = rep(1,length(year_continuous)))
save(cp_results_rodent5, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_5.Rds'))
rm(cp_results_rodent5)

cp_results_rodent6 = changepoint_model(ldats_lda_selected[[1]], x, 6, weights = rep(1,length(year_continuous)))
save(cp_results_rodent6, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_6.Rds'))
rm(cp_results_rodent6)
```

```{r select LDATS LDA and paper cpt}
#### Changepoint model selection ####
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_1.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_2.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_3.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_4.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_5.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_6.Rds'))

@@

#### Load LDA ####
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_ldamodel.Rds'))

@@

```{r run paper LDA and paper cpt, eval = F}
#### Run changepoint ####
source(here::here('vignettes', 'christensenetal-comparison-files', 'christensenetal-2018-files', 'changepointmodel.r'))

@@

# run models with 1, 2, 3, 4, 5, 6 changepoints
cp_results_rodent = changepoint_model(ldamodel, x, 1, weights = rep(1,length(year_continuous)))
save(cp_results_rodent, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper1.Rds'))
rm(cp_results_rodent)

cp_results_rodent2 = changepoint_model(ldamodel, x, 2, weights = rep(1,length(year_continuous)))
save(cp_results_rodent2, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper2.Rds'))
rm(cp_results_rodent2)

cp_results_rodent3 = changepoint_model(ldamodel, x, 3, weights = rep(1,length(year_continuous)))
save(cp_results_rodent3, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper3.Rds'))
rm(cp_results_rodent3)

cp_results_rodent4 = changepoint_model(ldamodel, x, 4, weights = rep(1,length(year_continuous)))
save(cp_results_rodent4, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper4.Rds'))
rm(cp_results_rodent4)

cp_results_rodent5 = changepoint_model(ldamodel, x, 5, weights = rep(1,length(year_continuous)))
save(cp_results_rodent5, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper5.Rds'))
rm(cp_results_rodent5)

cp_results_rodent6 = changepoint_model(ldamodel, x, 6, weights = rep(1,length(year_continuous)))
save(cp_results_rodent6, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper6.Rds'))
rm(cp_results_rodent6)
```

```{r select paper LDA and paper cpt}
#### Changepoint model selection ####
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_1.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_2.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_3.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_4.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_5.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_6.Rds'))

@@

save(ldats_ldats_cpt, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_ldats.Rds'))
rm(ldats_ldats_cpt)
rm(ldats_lda_selected)
```

```{r load LDATS LDA and LDATS changepoint, include = F}
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_ldats.Rds'))
```

@@

save(ldats_ldats_cpt_selected, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_ldats_selected.Rds'))

@@

save(paper_ldats_cpt, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_ldats.Rds'))
rm(paper_ldats_cpt)
rm(ldamodel)
```

```{r load paper LDA and LDATS changepoint, include = F}
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_ldats.Rds'))
```

@@

Unlike the paper changepoint model, LDATS can recognize that sampling periods may not be equidistant, and can place changepoint estimates at new moons if they fall between nonconsecutive sampling periods. We can estimate the dates corresponding to those new moons, extrapolating from the census dates for adjacent census periods.

@@

save(paper_ldats_cpt_selected, file = here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_ldats_selected.Rds'))

@@

```{r load cpts to plot, include = F}
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_ldats_selected.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_ldats_selected.Rds'))
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'paper_paper_4.Rds'))
paper_paper_cpt_selected <- cp_results_rodent4
load(here::here('vignettes', 'christensenetal-comparison-files', 'model-cache', 'ldats_paper_4.Rds'))
ldats_paper_cpt_selected <- cp_results_rodent4

#### Paper LDA and LDATS changepoint

```{r plot paper LDA and LDATS cpts, fig.width=6, fig.height=6}

#### LDATS LDA and LDATS changepoint
```{r plot ldats LDA and LDATS cpt, fig.width=6, fig.height=6}
plot(ldats_ldats_cpt_selected)
```

#### Paper LDA and paper changepoint
```{r plot paper LDA and paper cpt, fig.width=6, fig.height=6}

source(here::here('vignettes', 'christensenetal-comparison-files', 'christensenetal-2018-files', 'LDA_figure_scripts.R'))
source(here::here('vignettes', 'christensenetal-comparison-files', 'christensenetal-2018-files', 'changepointmodel.r'))
paper_cpts = find_changepoint_location(paper_paper_cpt_selected)
paper_cpt_plot = get_ll_non_memoized_plot(ldamodel,x,paper_cpts,make_plot=T,weights=rep(1,length(year_continuous)))
annual_hist(paper_paper_cpt_selected, year_continuous)
paper_cpt_plot

#### LDATS LDA and paper changepoint
```{r plot LDATS lda and paper cpt, fig.width=6, fig.height=6}
ntopics = 6
ldats_cpts = find_changepoint_location(ldats_paper_cpt_selected)
ldats_cpt_plot = get_ll_non_memoized_plot(ldats_lda_selected[[1]],x,ldats_cpts,make_plot=T,weights=rep(1,length(year_continuous)))
annual_hist(ldats_paper_cpt_selected, year_continuous)
ldats_cpt_plot
```

The results of the changepoint model appear extremely robust to both choice of LDA model and choice of changepoint model.

### Report changepoint dates
```{r report cpt dates, include = F}

@@

The choice of LDA has more influence on the changepoint locations than the choice of changepoint model - probably because the LDATS LDA has 6 topics, and the paper LDA has 4. However, all of the models agree to within 6 months in most cases, and a year for the broader early 1990s changepoint.

@@
